Portfolio conservation of metapopulations\\under climate change

### 2013-08-28 inst/ms/ms.tex
Minor tweaks to ms; mostly in abstract

\begin{itemize}
\item
  The introduction may be a bit literature heavy. (We also need to cut 11 references to get to 50.)
\item
  The main message may be a bit repetitive throughout.
\item
  I wish I didn't have so many paragraphs with numbered lists, but am struggling to work around that.
\item
  I think there is room for expansion of the discussion (we still have \textasciitilde{}500 words to play with). The discussion could benefit from bringing in more concrete examples of how this ties in with PNW salmon and I welcome your ideas here. If we have space we could also discuss our results in the context of response diversity literature.
\item
  The supplementary figures and captions aren't finished but should be quick to generate.
\item
  I will write a short vignette describing how to use the R package like I did for the Methods in Ecology and Evolution paper.
\item
  I will submit the \texttt{.pdf} version; the \texttt{.docx} version is for you to edit with Track Changes, if you'd like. Only the \texttt{.pdf} version contains the figures and if you can't see the equations in the \texttt{.docx} version (Andy?) then see the \texttt{.pdf} version.
\item
  We still need to discuss authorship and order of authorship.
\item
  Notes from Nick: (1) add something about how many of these concepts are key elements of conservation ecology, but they haven't been tested quantitatively before, (2) consider flipping the discussion around so the broad elements come first and the salmon applications come near the end, (3) consider sticking with ``one half/other half'', or ``lower half/upper half''. If lower/upper, need to explain reasoning.
\end{itemize}

@@

\emph{Words in abstract and main text}: (maximum 150, 5000)

\emph{Number of references}: (maximum 50)

\emph{Number of tables and figures}: 1, 5

@@

Managing risk is fundamental to the conservation of an endangered species. When an endangered species exists as a metapopulation, we typically manage risk at the subpopulation level. However, a portfolio approach might consider how conservation affects the ``weight'' of each population in a metapopulation ``portfolio''. Here we ask how such a portfolio approach can inform conservation priorities for metapopulations in a changing world. We develop a salmon metapopulation simulation in which population-specific productivity is driven by spatially-distributed thermal tolerance and patterns of short- and long-term environmental change. We then implement spatial conservation strategies that control subpopulation carrying capacities and evaluate the salmon portfolios along risk-return axes. We show that conserving response diversity minimizes risk given environmental stochasticity and ensures persistence given long-term environmental change. Further, conserving more subpopulations minimizes risk regardless of response diversity distribution. These findings have important implications for how we prioritize metapopulation conservation and emphasize the importance of conserving the processes that promote response diversity.

@@

Managing risk is fundamental to conserving endangered species \citep{burgman2005, iucn2009}. When an endangered species exists as a metapopulation, we can manage risk at two levels: at the population level or at the metapopulation level. Typically we treat sources of risk at the metapopulation level as exogenous and manage risk at the population level by manipulating hunting or fishing levels, implementing reserves, or improving connectivity \citep[e.g.][]{akcakaya2007}.

>>>>

\begin{itemize}
\item
  The introduction may be a bit literature heavy. (We also need to cut 11 references to get to 50.)
\item
  The main message may be a bit repetitive throughout.
\item
  I wish I didn't have so many paragraphs with numbered lists, but am struggling to work around that.
\item
  I think there is room for expansion of the discussion (we still have \textasciitilde{}500 words to play with). The discussion could benefit from bringing in more concrete examples of how this ties in with PNW salmon and I welcome your ideas here. If we have space we could also discuss our results in the context of response diversity literature.
\item
  The supplementary figures and captions aren't finished but should be quick to generate.
\item
  I will write a short vignette describing how to use the R package like I did for the Methods in Ecology and Evolution paper.
\item
  I will submit the \texttt{.pdf} version; the \texttt{.docx} version is for you to edit with Track Changes, if you'd like. Only the \texttt{.pdf} version contains the figures and if you can't see the equations in the \texttt{.docx} version (Andy?) then see the \texttt{.pdf} version.
\item
  We still need to discuss authorship and order of authorship.
\item
  Notes from Nick: (1) add something about how many of these concepts are key assumptions of conservation ecology, but they haven't been tested quantitatively before, (2) consider flipping the discussion around so the broad elements come first and the salmon applications come near the end, (3) consider sticking with ``one half/other half'', or ``lower half/upper half''. If lower/upper, need to explain reasoning.
\end{itemize}

@@

\emph{Words in abstract and main text}: 153, 4100 (maximum 150, 5000)

\emph{Number of references}: 61 (maximum 50)

\emph{Number of tables and figures}: 5 (maximum 6)

@@

Managing risk is fundamental to conserving endangered species. When an endangered species exists as a metapopulation, we typically manage risk at the subpopulation level. However, a portfolio approach might consider how conservation affects the ``weight'' of each population in a metapopulation ``portfolio''. Here we ask how a portfolio approach can inform conservation priorities for metapopulations in a changing world. We develop a salmon metapopulation simulation where population-specific productivity is driven by spatially-distributed thermal tolerance and patterns of short- and long-term environmental change. We then implement spatial conservation strategies that control subpopulation carrying capacities and evaluate the salmon portfolios along risk-return axes. We show that conserving response diversity minimizes risk given environmental stochasticity and ensures persistence given long-term environmental change. Further, conserving more subpopulations minimizes risk regardless of response diversity distribution. These findings have important implications for how we prioritize metapopulation conservation and emphasize the importance of conserving the processes that promote response diversity.

@@

Managing risk is fundamental to the conservation of an endangered species \citep{burgman2005, iucn2009}. When an endangered species exists as a metapopulation, we can manage risk at two levels: at the population level or at the metapopulation level. Typically we treat sources of risk at the metapopulation level as exogenous and manage risk at the population level by manipulating hunting or fishing levels, implementing reserves, or improving connectivity \citep[e.g.][]{akcakaya2007}.
